\simname 2.0 User's Guide

### 2008-08-28 doc/manual.tex
Added physical subnetworks. Added progressive adaptive in UGAL. Non-minimal and minimal traffic classes in valiant and UGAL FBFly. Deadlock warning counter. Flip a coin for generation always. Note: It appears to deadlock if wait_for_tail_flits is disabled.
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@638 ce7aba0d-9f81-40a6-a495-cecae84b0515

\author{Ted Jiang, Brian Towles and William J. Dally}
\title{\simname 2.0 User's Guide}

@@

>>>>

\author{Ted Jiang, Brian Towles, George Michelogiannakis and William J. Dally}
\title{\simname 2.0 User's Guide}

@@

\subsection{Physical sub-networks}
\label{sec:physical_subnets}

The \texttt{physical\_subnetworks} parameter defines the number of physical sub-networks present in the network (defaults to one).
All sub-networks receive the same configuration parameters and thus are identical. Traffic sources
maintain an injection queue for each sub-network. The packet generation process is unaffected. It enqueues generated packets into the
proper sub-network queue according to a division function in the traffic manager. At every cycle, flits at the head of each queue attempt to be injected.
Traffic destinations can eject one flit from each sub-network each cycle.
